% ตัวอย่างรายการบรรณานุกรมแบบ manual
\begin{thebibliography}{99}
    \bibitem{ragsdale2008} Ragsdale, C. T. (2008). 
        \textit{Spreadsheet Modeling \& Decision Analysis: A Practical Introduction to Business Analytics} 
        (6th ed., Chapter~13: Queuing Theory). Cengage Learning.
    \bibitem{kelton2010} Kelton, W. D., Sadowski, R. P., \& Sadowski, D. A. (2010). 
        \textit{Simulation with Arena} (2nd ed.). McGraw-Hill Education (Asia) / McGraw-Hill.
	\bibitem{ref3} Sasibhushana Matcha, et al. (2025). 
    RESTful API Design and Implementation: Best Practices for Building Scalable and Maintainable Web Services. 
    ResearchGate. Retrieved from \url{https://www.researchgate.net/publication/388950588_RESTful_API_Design_and_Implementation_Best_Practices_for_Building_Scalable_and_Maintainable_Web_Services}
	\bibitem{babulak2008} Babulak, E., \& Wang, M. (2008). Discrete event simulation: State of the art. \textit{International Journal of Online Engineering (iJOE)}, 4(1), 60–63. \url{https://doi.org/10.5772/9894}
    \bibitem{rich2023} Rich, J. (2023). Fixed routing or demand-responsive? Agent-based modeling of autonomous vehicle services for first and last mile connections. \textit{Transportation Research Part C: Emerging Technologies}, 145, Article 104598. \url{https://doi.org/10.1016/j.trc.2023.104598}
    \bibitem{ref4} ธัญญลักษณ์ สามภูศรี, ยุคนธร คงปฐมพงศ์ \& ยุภาพร ตงประสิทธิ์. (n.d.). บทบาทของกระบวนการเกิดและตายในทฤษฎีแถวคอย = The role of the birth and death in queueing theory [PDF]. สาขาสารสนเทศสถิติ คณะวิทยาศาสตร์ มหาวิทยาลัยขอนแก่น. Retrieved from \url{https://sc2.kku.ac.th/stat/statweb/images/Eventpic/60/Seminar/02_7_.pdf}
\end{thebibliography}

% หากใช้ BibTeX ให้แทนที่ด้วย
% \bibliographystyle{plain}